Manuscript Figures

### 2021-06-01 src/manuscript_figures.Rmd
update pancancer benchmark figure panels

dt <- data.table(melt(pancancer_stats))[Var1 %in% c('Mean_Balanced_Accuracy')]
dt$Var2 <- toupper(gsub("_factors", "", dt$Var2))
p1 <- ggplot(dt, aes(x = Var2, y = value)) + 
  geom_bar(stat = 'identity', aes(fill = Var2)) + 
  labs(y = 'Mean Balanced Accuracy') + 
  theme(legend.title = element_blank(), axis.title.x = element_blank())

@@

# plot cancer specific factors
M <- LFs$maui_factors$pancancer.cnv_gex_meth_mut
ct <- surv[match(rownames(M), bcr_patient_barcode)]$project
p3 <- plot_label_specific_vars(M, ct)

@@

Fig <- plot_grid(plot_grid(p1, p2, p5, nrow = 1, labels = c('A', 'B', 'C')), 
                  plot_grid(p3, p4, rel_widths = c(5,3), nrow = 1, labels = c('D', 'E')), 
                  nrow = 2,
                  rel_heights = c(2,3))

>>>>

dt <- data.table(melt(pancancer_stats))[Var1 %in% c('Mean_Balanced_Accuracy')]
dt$Var2 <- toupper(gsub("_factors", "", dt$Var2))
p1 <- ggplot(dt, aes(x = Var2, y = value)) + 
  geom_bar(stat = 'identity', aes(fill = Var2)) + 
  labs(y = 'Mean Balanced Accuracy') + 
  theme(legend.title = element_blank(), axis.title.x = element_blank(), 
        axis.text = element_text(size = 14), axis.title = element_text(size = 16))

@@

# plot cancer specific factors
M <- LFs$maui_factors$pancancer.cnv_gex_meth_mut
ct <- surv[match(rownames(M), bcr_patient_barcode)]$project

p3 <- plot_label_specific_vars(M, ct)

@@

Fig <- plot_grid(plot_grid(p1, p2$gtable, nrow = 1, labels = c('A', 'B')), 
                  plot_grid(p3, p4, nrow = 1, labels = c('C', 'D')), 
                  nrow = 2,
                  rel_heights = c(2,3))
